### 2022-11-01 chapters/background.tex
minor edits

\begin{remark}
	ER-SSAT problem is $\mathrm{NP}^{\mathrm{PP}}$-hard whereas RE-SSAT problem is $\mathrm{PP}^{\mathrm{NP}}$-complete~\cite{littman2001stochastic}.
\end{remark}

>>>>

\begin{remark}
	The decision problem of ER-SSAT is $\mathrm{NP}^{\mathrm{PP}}$ whereas RE-SSAT problem is $\mathrm{PP}^{\mathrm{NP}}$-complete~\cite{littman2001stochastic}.
\end{remark}
